SunPy - Python for Solar Physics

### 2014-01-30 1-Introduction.tex
removed ack

The purpose of this paper is to provide an overview of SunPy's current 
capabilities, an overview of the project's development model, community aspects of the 
project, and future plans. The latest release of SunPy, version 0.4,
can be downloaded from \href{http://sunpy.org}{www.sunpy.org} or can be
installed using the \href{http://pypi.python.org/pypi}{Python package index}.

>>>>

The purpose of this paper is to provide an overview of SunPy's current 
capabilities, an overview of the project's development model, community aspects of the 
project, and future plans. The latest release of SunPy, version 0.4,
can be downloaded from \url{http://sunpy.org} or can be
installed using the Python package index (\url{http://pypi.python.org/pypi}).

### 2014-01-30 2-2-Lightcurve.tex
added lines to GOES lightcurve code example
more updates to GOES lightcurve code block.
removed ack

Currently, the \texttt{LightCurve} class is compatible with the
following data sources: the \textit{GOES} X-ray Sensor (XRS), \textit{PROBA2}/LYRA, and
the \textit{SDO} EUV Variability Experiment (EVE; only the level ``OCS'' and
% Do we need to explain what OCS means?
% RJH: I'd argue that everything other than (EVE) can be cut, but I'm not 
% confident enough to make that cut.
% dps: I agree, JI, what do you think?
average CSV files -- see \url{http://lasp.colorado.edu/home/eve/data/}
for more detail).  For each of these instruments, a subclass of the
\texttt{LightCurve} object is initialised
(e.g., \texttt{GOESLightCurve}) which inherits from
\texttt{LightCurve} but allows instrument-specific functionality to be
included.  Future developments will introduce support for additional
instruments and data products, as well as implementing a factory interface 
similar to that of \texttt{Map}.  Since there is no established standard
as to how time-series data should be stored and distributed, each SunPy 
\texttt{LightCurve} object sub-class provides the ability to download its corresponding 
specific data format in its constructor and parse that file type.

@@

%removed the resample part of the example - really we need to fix truncate!
% schriste - i think it would be better to show off some of the powerful pandas methods in this section
% as we are not likely to fix truncate and i think it should be refactored anyway
%ays: moved these comments outside of the listing in case we forget to delete these
\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy import lightcurve
>>> from sunpy.time import TimeRange
>>> goes = lightcurve.GOESLightCurve.create('2011-06-07 06:00',
...                                         '2011-06-07 08:00')
>>> goes.peek()
\end{minted}
\begin{center}
\includegraphics[width=10cm]{goes_lightcurve.pdf}
\end{center}
\caption{Example retrieval of a GOES lightcurve
using a time range, and the output of the 
\texttt{peek()} method.}
\label{code:goes_lc}
\end{listing}

>>>>

Currently, the \texttt{LightCurve} class is compatible with the
following data sources: the \textit{GOES} X-ray Sensor (XRS), \textit{PROBA2}/LYRA, and \textit{SDO}/EVE\footnote{Note that only the level ``OCS'' and
average CSV files is currently implemented -- see \url{http://lasp.colorado.edu/home/eve/data/}}.  For each of these instruments, a subclass of the
\texttt{LightCurve} object is initialised
(e.g., \texttt{GOESLightCurve}) which inherits from
\texttt{LightCurve} but allows instrument-specific functionality to be
included.  Future developments will introduce support for additional
instruments and data products, as well as implementing a factory interface 
similar to that of \texttt{Map}.  Since there is no established standard
as to how time-series data should be stored and distributed, each SunPy 
\texttt{LightCurve} object sub-class provides the ability to download its corresponding 
specific data format in its constructor and parse that file type.

@@

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy import lightcurve
>>> from sunpy.time import TimeRange
>>> goes = lightcurve.GOESLightCurve.create('2011-06-07 06:00',
...                                         '2011-06-07 08:00')
>>> goes.peek()
\end{minted}
\begin{center}
\includegraphics[width=10cm]{goes_lightcurve.pdf}
\end{center}
\caption{Example retrieval of a GOES lightcurve
using a time range, and the output of the 
\texttt{peek()} method.}
\label{code:goes_lc}
\end{listing}

### 2014-01-30 2-Data_Types.tex
removed ack

These classes allow access to the data
and associated metadata and provide appropriate convenience functions to
enable analysis and visualisation. For each of these classes, the data is
stored in the \texttt{data} attribute while the metadata should be stored 
in the \texttt{meta} attribute. (Curently, only \texttt{Map} has this feature 
fully implemented.) 
% schriste - can't we just quickly fix this? should be easy enough.
% dps - Spectrogram does not contain meta either! I would suggest
%(Curently, this is just supported by Map, but the other data types will 
%include such attribute soon.)
%SJM: oh what, drop it all together.
%SJM see PR #785 to the main repo.
It is possible to instantiate the
data types from various
different sources: e.g., files, URLs, arrays.  
In order to provide instrument-specific specialisation, the core SunPy classes 
make use of subclassing; e.g., \texttt{Map} has an \texttt{AIAMap} 
sub-type for data from the \textit{SDO}/AIA instrument.

>>>>

These classes allow access to the data
and associated metadata and provide appropriate convenience functions to
enable analysis and visualisation. For each of these classes, the data is
stored in the \texttt{data} attribute while the metadata should be stored 
in the \texttt{meta} attribute (currently, only \texttt{Map} has this feature 
fully implemented). 
% schriste - change this until all fixed
It is possible to instantiate the
data types from various
different sources: e.g., files, URLs and arrays.  
In order to provide instrument-specific specialisation, the core SunPy classes 
make use of subclassing; e.g., \texttt{Map} has an \texttt{AIAMap} 
sub-type for data from the \textit{SDO}/AIA instrument.
